---
title: "p8105_hw5_lk2776"
output: html_document
date: "2024-11-05"
---

#Problem 2 
```{r}
library(tidyverse)
library(purrr)
library(broom)
library(ggplot2)
```

```{r}
#function
sim_mean_sd = function(n =30, mu, sigma = 5) {
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma)
)
  
  t_test_out <- t.test(sim_data$x, mu = 0) #null 
  
  tidy(t_test_out)|>
    select(estimate, p.value) 
}
#Run function on data mu = 0
sim_results_df =
  expand_grid(
    mu_given = 0,
    iter = 1:5000
  ) |>
  mutate(
    estimate_df = map(mu_given, \(x) sim_mean_sd(mu = x))
  ) |>
  unnest(estimate_df)
```


```{r}
#Run function on data 
sim_results_df_b =
  expand_grid(
    #sample_size = 30,
    mu_given = c(1,2,3,4,5,6),
    iter = 1:5000
  ) |>
  mutate(
    estimate_df = map(mu_given, \(x) sim_mean_sd(mu = x))
  ) |>
  unnest(estimate_df)
sim_results_df_all <- bind_rows(sim_results_df,sim_results_df_b)
```

As shown in the plot below, as the true value of mu increases, the power of the test also increases and reaches 1. 


effect size is defined as the difference between sample mean  and hypothesized mean(mu = 0). Therefore, as true mean increases, the effect size increases, the power of the test also increases and test is more likely to correctly reject the null hypothesis. 




```{r}
new_df = sim_results_df_all |>
  mutate(reject_null = p.value < 0.05) |>
  group_by(mu_given) |>
  summarise(power_calc = mean(reject_null)) #power for each value of mu # proportion of times the null was rejected. 
  
ggplot(new_df,aes(x = mu_given, y = power_calc)) +
  geom_point() +
  geom_line() +
  labs(
    title = "power against true value of mu",
    x = "true mu",
    y = "power"
  )
```

As shown in the plot below, the sample average of mu-hat across tests for which is rejected is not to equal to true value of mu at low value of mu. 
```{r}
new_df_b = sim_results_df_b |>
  group_by(mu_given) |>
  summarize(
    avg_mu_hat = mean(estimate),
    avg_mu_hat_rejected = mean(estimate[p.value <0.05]))

ggplot(new_df_b, aes(x = mu_given))+
  geom_line(aes(y=avg_mu_hat),color="blue", size = 1) +
  geom_line(aes(y=avg_mu_hat_rejected), color="orange", size =1)+
  labs(
    title = "average mu-hat vs true mu",
    x = "true mu",
    y = "average mu-hat", 
  ) +
  annotate("text", x = 4.7, y = 2, label = "samples with rejected null", color = "orange") +
  annotate("text", x = 4.9, y = 2.25, label = "all samples", color = "blue")

```


## problem3

```{r}
#read data
data = read_csv("./data/homicide-data.csv") |>
  janitor::clean_names() |>
  drop_na()
```

The number of rows and columns in the homicides data: **`r dim_desc(data)`** 
The column variables are: **`r colnames(data)`** . The dataset includes information about victim, reported date of homicide, location of homicide, and status of the case. 

```{r}
summary_data = data |>
  mutate(city_state = paste(city, state, sep="_"), 
         not_solved = if_else(
           disposition %in% c("Closed without arrest", "Open/No arrest"), 1, 0))  |> # if match, add 1, otherwise, add 0. 
  group_by(city_state) |>
  summarize(
    total_number_of_homicides = n(), #count
    unsolved_homicides = sum(not_solved) 
  ) #|>
  #knitr::kable()
head(summary_data)
```

```{r}
#baltimore prop test
summary_data_baltimore = summary_data |>
  filter(city_state == "Baltimore_MD") 

prop_test_out_balti = prop.test(summary_data_baltimore$unsolved_homicides,summary_data_baltimore$total_number_of_homicides)

tidy(prop_test_out) |>
  select(estimate,conf.low,conf.high) |>
  knitr::kable()
         
```

```{r}
#all cities prop test
prop_results_all_cities = summary_data |>
  mutate(prop_test_out_all = map2(unsolved_homicides,total_number_of_homicides, \(x,y) prop.test(x,y)),
         tidy_df = map(prop_test_out_all,tidy))|>
  unnest(tidy_df) |>
  select(city_state,estimate,conf.low,conf.high)
  
prop_results_all_cities |>
 mutate(city_state = fct_reorder(city_state,estimate)) |>
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point(color="purple") +
  geom_errorbar(aes(ymin=conf.low, ymax = conf.high), color = "orange") +
  coord_flip() + #to facilitate the viewing - otherwise - x-axis crowded
  labs(
    title = "proportion of unsolved homicides",
    x = "estimate",
    y = "city and state", 
  )
```
