---
title: "p8105_hw5_lk2776"
output: html_document
date: "2024-11-05"
---
```{r setup, warning=FALSE,message=FALSE}
#load packages
library(tidyverse)
library(ggridges)
library(patchwork)
library(purrr)
library(broom)
library(ggplot2)

#R figure settings
knitr::opts_chunk$set(
  fig.width = 9,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

#problem 2 

```{r}
#function
sim_mean_sd = function(n =30, mu, sigma = 5) {
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma)
)
  
  t_test_out <- t.test(sim_data$x, mu = 0) #null 
  
  tidy(t_test_out)|>
    select(estimate, p.value) 
}
#Run function on data mu = 0
sim_results_df =
  expand_grid(
    mu_given = 0,
    iter = 1:5000
  ) |>
  mutate(
    estimate_df = map(mu_given, \(x) sim_mean_sd(mu = x))
  ) |>
  unnest(estimate_df)
```


```{r}
#Run function on data 
sim_results_df_b =
  expand_grid(
    #sample_size = 30,
    mu_given = c(1,2,3,4,5,6),
    iter = 1:5000
  ) |>
  mutate(
    estimate_df = map(mu_given, \(x) sim_mean_sd(mu = x))
  ) |>
  unnest(estimate_df)
sim_results_df_all <- bind_rows(sim_results_df,sim_results_df_b)
```

As shown in the plot below, as the true value of mu increases, the power of the test also increases, reaching 1. Effect size is defined as the difference between sample mean and the hypothesized mean(mu = 0). Therefore, as the true mean increases, the effect size becomes larger. This increase in effect size, increases the ability of the test to correctly detect the true effect and correctly reject the null hypothesis. As a result, power of the test also increases with larger true mean values. 

```{r}
new_df = sim_results_df_all |>
  mutate(reject_null = p.value < 0.05) |>
  group_by(mu_given) |>
  summarise(power_calc = mean(reject_null)) #power for each value of mu # proportion of times the null was rejected. 
  
ggplot(new_df,aes(x = mu_given, y = power_calc)) +
  geom_point() +
  geom_line() +
  labs(
    title = "power against true value of mu",
    x = "true mu",
    y = "power"
  )
```

As shown in the plot below, the sample average of mu-hat across tests for which null is rejected (orange line) is not ~equal to true value of mu due to selection bias (selecting tests where null hypothesis is rejected, this usually happens when mu-hat is farther away from hypothesized mean). By selecting only significant results, the analysis failed to consider the non-significant results that may contain mu-hat closer to true mu.  


```{r}
new_df_b = sim_results_df_b |>
  group_by(mu_given) |>
  summarize(
    avg_mu_hat = mean(estimate),
    avg_mu_hat_rejected = mean(estimate[p.value <0.05]))

ggplot(new_df_b, aes(x = mu_given))+
  geom_line(aes(y=avg_mu_hat),color="blue", size = 1) +
  geom_line(aes(y=avg_mu_hat_rejected), color="orange", size =1)+
  labs(
    title = "average mu-hat vs true mu",
    x = "true mu",
    y = "average mu-hat", 
  ) +
  annotate("text", x = 4.7, y = 2, label = "samples with rejected null", color = "orange") +
  annotate("text", x = 4.9, y = 2.25, label = "all samples", color = "blue")

```

## problem3

```{r}
#read data
data = read_csv("./data/homicide-data.csv") |>
  janitor::clean_names() |>
  drop_na()
```

The number of rows and columns in the homicides data: **`r dim_desc(data)`** 
The column variables are: **`r colnames(data)`** . The dataset includes information about victim, reported date of homicide, location of homicide, and status of the case. 

```{r}
summary_data = data |>
  mutate(city_state = paste(city, state, sep="_"), 
         not_solved = if_else(
           disposition %in% c("Closed without arrest", "Open/No arrest"), 1, 0))  |> # if match, add 1, otherwise, add 0. 
  group_by(city_state) |>
  summarize(
    total_number_of_homicides = n(), #count
    unsolved_homicides = sum(not_solved) 
  ) #|>
  #knitr::kable()
head(summary_data)
```

```{r}
#baltimore prop test
summary_data_baltimore = summary_data |>
  filter(city_state == "Baltimore_MD") 

prop_test_out_balti = prop.test(summary_data_baltimore$unsolved_homicides,summary_data_baltimore$total_number_of_homicides)

tidy(prop_test_out_balti) |>
  select(estimate,conf.low,conf.high) |>
  knitr::kable()
         
```

```{r}
#all cities prop test
prop_results_all_cities = summary_data |>
  mutate(prop_test_out_all = map2(unsolved_homicides,total_number_of_homicides, \(x,y) prop.test(x,y)),
         tidy_df = map(prop_test_out_all,tidy))|>
  unnest(tidy_df) |>
  select(city_state,estimate,conf.low,conf.high)
  
prop_results_all_cities |>
 mutate(city_state = fct_reorder(city_state,estimate)) |>
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point(color="purple") +
  geom_errorbar(aes(ymin=conf.low, ymax = conf.high), color = "orange") +
  coord_flip() + #to facilitate the viewing - otherwise - x-axis crowded
  labs(
    title = "proportion of unsolved homicides",
    x = "estimate",
    y = "city and state", 
  )
```
